Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-09-05 Manuscript/manuscript.tex
Added relative surface excess for L14+Aqvist into the MS with corresponding data into Data folder. Added a simple info-graphic (conceptual!) for the description of bindin sites in POPC. Only ECC-lipids model is presented (it's the simplest) Manuscript includes the new figure.

Significant improvement is achieved with the newly developed ECC-lipid model. 
The head group order parameter changes as a function of CaCl$_2$
concentration show a good agreement between ECC-lipid model and 
experiments in Fig. \ref{OrderParameterCHANGESnewMODELS}.
Ion binding affinity is quantified by using the relative surface
excess between ions and water from Eq.~\ref{surfexcess} and  
density profiles along membrane normal shown in Fig.~\ref{fig:cacl-dens}.
%This is directly related to the amount of surface excess charge 
%as shown along with ion density profiles in  Fig.~\ref{fig:cacl-dens}.
The relative surface excess for ECC-lipid model with ECC-ions $\Gamma_i^w = 0.07 nm^{-3}$
is significantly smaller than for Lipid14 with \AA{}qvist $\Gamma_i^w = XX nm^{-3}$
and Dang ions $\Gamma_i^w = 0.3 nm^{-3}$.
\todo{JOE: Add error estimates to Gamma values}
%The density profiles from simulations with original Lipid14 \cite{dickson14}
%and Dang ions \cite{smith94,chang1999,dang2006} 
%show a pronounced peak in the position of the phosphate moieties of POPC. 
%The use of ECC-ion model~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
%or the ion model by \AA{qvist}~\cite{aqvist90}
%along with Lipid14 does not significantly change it 
%(Headgroup order parameter responses for these models in SI).
%The new ECC-lipids model with ECC-ions~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
%exhibits on the other hand smaller density in this region 
%suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
%It is then likely that the models that overestimate head group order parameter response~\cite{catte16}
%also overestimate the amount of bound cations.
\todo{This paragraph is to be finalized when we have the surface excess analysis
  done by using Eq.~\ref{surfexcess}.}

@@

>>>>

Significant improvement is achieved with the newly developed ECC-lipid model. 
The head group order parameter changes as a function of CaCl$_2$
concentration show a good agreement between ECC-lipid model and 
experiments in Fig. \ref{OrderParameterCHANGESnewMODELS}.
Ion binding affinity is quantified by using the relative surface
excess between ions and water from Eq.~\ref{surfexcess} and  
density profiles along membrane normal shown in Fig.~\ref{fig:cacl-dens}.
%This is directly related to the amount of surface excess charge 
%as shown along with ion density profiles in  Fig.~\ref{fig:cacl-dens}.
The relative surface excess for ECC-lipid model with ECC-ions $\Gamma_i^w = 0.07 nm^{-3}$
is significantly smaller than for Lipid14 with \AA{}qvist $\Gamma_i^w = 0.13 nm^{-3}$
and Dang ions $\Gamma_i^w = 0.3 nm^{-3}$ (error estimate being below 10\%).
%The density profiles from simulations with original Lipid14 \cite{dickson14}
%and Dang ions \cite{smith94,chang1999,dang2006} 
%show a pronounced peak in the position of the phosphate moieties of POPC. 
%The use of ECC-ion model~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
%or the ion model by \AA{qvist}~\cite{aqvist90}
%along with Lipid14 does not significantly change it 
%(Headgroup order parameter responses for these models in SI).
%The new ECC-lipids model with ECC-ions~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
%exhibits on the other hand smaller density in this region 
%suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
%It is then likely that the models that overestimate head group order parameter response~\cite{catte16}
%also overestimate the amount of bound cations.
\todo{This paragraph is to be finalized when we have the surface excess analysis
  done by using Eq.~\ref{surfexcess}.
  JOE: Relative surface excess values are there, so let's finalize it.}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[height=6.0cm]{../Fig/POPC_binding_labels.eps} 
  \includegraphics[height=6.0cm]{../Fig/POPC_binding_ECC-lipids.eps}
  \caption{\label{fig:binding_conf}
      Configurations of \ce{Ca2+} binding in POPC membranes in the ECC-lipids model.
      The binding sites are: 
      red circle for phosphate oxygens; 
      blue square for sn-1 carbony oxygen; and green triangle for sn-2 carbonyl oxygen.
      The configurations along with their probabilities are drawn in the following manner:
      each row corresponds to an individual lipid the cation is bound to;
      symbols denote the site the cations is bound to the respective lipid.
      An empty configuration denotes an unbound cation in a solvent. 
  }
\end{figure}
